---
title: "Homework 6"
author: "Alexis Colangelo"
date: "11/17/2019"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(modelr)
library(mgcv)


knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
  )

  options(
    ggplot2.continuous.colour = "viridis",
    ggplot2.continuous.fill = "viridis"
  )
  
  scale_colour_discrete = scale_colour_viridis_d
  scale_fill_discrete = scale_fill_viridis_d
  
  theme_set(theme_minimal() + theme(legend.position = "bottom"))
  
```

# Problem 1

## Load and clean the data for regression analysis:

```{r}
birthweight_data = read_csv(file = "./data/birthweight.csv") %>%
  mutate(
    babysex = 
      recode(babysex, "1" = "male", "2" = "female"),
      babysex = factor(babysex),
    fincome = factor(fincome),
    frace = 
      recode(frace, "1" = "white", "2" = "black", 
             "3" = "asian", "4" = "puerto_rican", 
             "8" = "other", "9" = "unknown"),
      frace = factor(frace),
    malform = 
      recode(malform, "0" = "absent", "1" = "present"),
      malform = factor(malform),
    mrace =
      recode(mrace, "1" = "white", "2" = "black",
             "3" = "asian", "4" = "puerto_rican",
             "8" = "other"),
      mrace = factor(mrace)
  ) %>% view()
```

There are no missing data in this datset:
```{r}
table(is.na(birthweight_data))
```

## Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. 

```{r}
model_1 = step(lm(bwt ~., data = birthweight_data), direction = "backward")
```

By using the backwards elimination method, the regression model I propose is:
bwt = babysex + bhead + blength + delwt + gaweeks + mheight + mrace + parity + ppwt + smoken
    
## Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.
The backwards elimination procedure starts with the full model and the least significant variables. According to the scatterplot, we can see that the residuals are pretty evenly
spread out around zero, but there are some outliers. 
 
```{r}
model_1_data =
    birthweight_data %>% 
    select(
     babysex, bhead, blength, delwt, gaweeks, mheight, 
     mrace, parity, ppwt, smoken, bwt) 

model_1_plot =
  model_1_data %>%
  modelr::add_residuals(model_1) %>%
  modelr::add_predictions(model_1) %>%
  ggplot(aes(x = pred, y = resid)) + geom_point()

model_1_plot

```

## Compare your model to two others:
* One using length at birth and gestational age as predictors (main effects only) 
* One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

Model 2 and 3 corresponding respectively to the above bullets:
```{r}
model_2 = lm(bwt ~ blength + gaweeks, birthweight_data)
model_3 = lm(bwt ~ bhead + blength + babysex + 
               bhead * blength + 
               bhead * babysex +
               blength * babysex + 
               bhead * blength * babysex, birthweight_data)
```

Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

```{r}
cv_bwt =
  crossv_mc(birthweight_data, 500) %>%
  mutate(
    train = map(train, as_tibble),
    test = map(test, as_tibble)
  )


cv_bwt = 
  cv_bwt %>% 
  mutate(
    model_1  = map(train, ~lm(bwt ~ babysex + bhead + blength + delwt + 
                  gaweeks + mheight + mrace + parity + ppwt + smoken, data = .x)),
    model_2 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
    model_3  = map(train, ~lm(bwt ~ bhead + blength + babysex + bhead * blength + 
               bhead * babysex +blength * babysex + bhead * blength * babysex, 
               data = .x))) %>% 
  
  mutate(
    rmse_model_1 = map2_dbl(model_1, test, ~rmse(model = .x, data = .y)),
    rmse_model_2 = map2_dbl(model_2, test, ~rmse(model = .x, data = .y)),
    rmse_model_3 = map2_dbl(model_3, test, ~rmse(model = .x, data = .y)))

cv_bwt %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model", 
    values_to = "rmse",
    names_prefix = "rmse_") %>% 
  mutate(model = fct_inorder(model)) %>% 
  ggplot(aes(x = model, y = rmse)) + geom_violin()
```

As we can see from the violin plot, by comparing all three of the models' root mean squared errors, it looks like model 1 (proposed model) sits the lowest on the graph, making it a better fit according to prediction error distributions. The next best model is model_3 (interaction effects).

# Problem 2

For this problem, we’ll use the 2017 Central Park weather data that we’ve seen elsewhere. The code chunk below (adapted from the course website) will download these data.

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

```

The boostrap is helpful when you’d like to perform inference for a parameter / value / summary that doesn’t have an easy-to-write-down distribution in the usual repeated sampling framework. We’ll focus on a simple linear regression with tmax as the response and tmin as the predictor, and are interested in the distribution of two quantities estimated from these data:
* r^2
* log(β^0 ∗ β^1)

Note: broom::glance() is helpful for extracting r^2 from a fitted regression, and broom::tidy() (with some additional wrangling) should help in computing log(β^0∗β^1).

## Use 5000 bootstrap samples and, for each bootstrap sample, produce estimates of these two quantities. 

Bootstrapping 5000 samples:
```{r}
set.seed(3)

boot_straps = 
  weather_df %>% 
  modelr::bootstrap(n = 5000) %>%
  mutate(
    models = map(strap, ~lm(tmax ~ tmin, data = .x) ),
    results_r = map(models, broom::glance),
    results_l = map(models, broom::tidy)) %>%
  select(-models, -strap) 

```

R-squared estimates:
```{r}
boot_straps_r =
  boot_straps %>%
  unnest(results_r) %>%
  select(.id, r.squared)

boot_straps_r
```

log(β^0 ∗ β^1) estimates:
```{r}
boot_straps_log =
  boot_straps %>%
  unnest(results_l) %>%
  select(.id, term, estimate) %>%
  pivot_wider(
    names_from = "term",
    values_from = "estimate") %>%
  mutate(
    log_results = log(`(Intercept)` * tmin))

boot_straps_log
```
  
## Plot the distribution of your estimates, and describe these in words. 

Distribution of R-squared estimates:
```{r}
plot_r = 
  boot_straps_r %>%
  ggplot(aes(x = r.squared)) + geom_histogram()

plot_r
```
This plot shows that the distribution of r-squared estimates from the bootstrapping are normally distributed.

Distribution of log(β^0 ∗ β^1) estimates:
```{r}
plot_log = 
  boot_straps_log %>%
  ggplot(aes(x = log_results)) + geom_histogram()

plot_log
```
This plot shows that the distribution of log(β^0 ∗ β^1) estimates from the bootstrapping are normally distributed.


## Using the 5000 bootstrap estimates, identify the 2.5% and 97.5% quantiles to provide a 95% confidence interval for r^2 and log(β^0∗β^1). 

r-squared:
```{r}
#lower limit = 0.8945
boot_straps_r %>%
  pull(r.squared) %>%
  quantile(0.025)

#upper limit = 0.9268
boot_straps_r %>%
  pull(r.squared) %>%
  quantile(0.975)
```
95% Confidence Interval for the r-squared estimates using the 5000 bootstraps is:
95% CI: (0.8945, 0.9268)


log(β^0∗β^1):
```{r}
#lower limit = 1.9651
boot_straps_log %>%
  pull(log_results) %>%
  quantile(0.025)

#upper limit = 2.0597
boot_straps_log %>%
  pull(log_results) %>%
  quantile(0.975)
```
95% Confidence Interval for the log(β^0∗β^1) estimates using the 5000 bootstraps is:
95% CI: (1.9651, 2.0597)
