---
title: "Homework 6"
author: "Alexis Colangelo"
date: "11/17/2019"
output: github_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
library(tidyverse)
library(rvest)
library(modelr)
library(mgcv)


knitr::opts_chunk$set(
  echo = TRUE,
  warning = FALSE,
  fig.width = 8,
  fig.height = 6,
  out.width = "90%"
  )

  options(
    ggplot2.continuous.colour = "viridis",
    ggplot2.continuous.fill = "viridis"
  )
  
  scale_colour_discrete = scale_colour_viridis_d
  scale_fill_discrete = scale_fill_viridis_d
  
  theme_set(theme_minimal() + theme(legend.position = "bottom"))
  
```

# Problem 1

## Load and clean the data for regression analysis:

```{r}
birthweight_data = read_csv(file = "./data/birthweight.csv") %>%
  mutate(
    babysex = 
      recode(babysex, "1" = "male", "2" = "female"),
      babysex = factor(babysex),
    fincome = factor(fincome),
    frace = 
      recode(frace, "1" = "white", "2" = "black", 
             "3" = "asian", "4" = "puerto_rican", 
             "8" = "other", "9" = "unknown"),
      frace = factor(frace),
    malform = 
      recode(malform, "0" = "absent", "1" = "present"),
      malform = factor(malform),
    mrace =
      recode(mrace, "1" = "white", "2" = "black",
             "3" = "asian", "4" = "puerto_rican",
             "8" = "other"),
      mrace = factor(mrace)
  ) %>% view()
```

There are no missing data in this datset:
```{r}
table(is.na(birthweight_data))
```

## Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. 

```{r}
model_1 = step(lm(bwt ~., data = birthweight_data), direction = "backward")
```

By using the backwards elimination method, the regression model I propose is:
bwt = babysex + bhead + blength + delwt + gaweeks + mheight + mrace + parity + ppwt + smoken
    
## Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.
The backwards elimination procedure starts with the full model and the least significant variables. According to the scatterplot, we can see that the residuals are pretty evenly
spread out around zero, but there are some outliers. 
 
```{r}
model_1_data =
    birthweight_data %>% 
    select(
     babysex, bhead, blength, delwt, gaweeks, mheight, 
     mrace, parity, ppwt, smoken, bwt) 

model_1_plot =
  model_1_data %>%
  modelr::add_residuals(model_1) %>%
  modelr::add_predictions(model_1) %>%
  ggplot(aes(x = pred, y = resid)) + geom_point()

model_1_plot

```

## Compare your model to two others:
* One using length at birth and gestational age as predictors (main effects only) 
* One using head circumference, length, sex, and all interactions (including the three-way interaction) between these

Model 2 and 3 corresponding respectively to the above bullets:
```{r}
model_2 = lm(bwt ~ blength + gaweeks, birthweight_data)
model_3 = lm(bwt ~ bhead + blength + babysex + 
               bhead * blength + 
               bhead * babysex +
               blength * babysex + 
               bhead * blength * babysex, birthweight_data)
```

Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.


